On the specific recursive structure of iterated parametricity

### 2025-11-11 paper/paper.tex
Mostly completing definitions + checking the indices

Formally, this can be described as:

@@

    \framep[n][0,...,p]                                                                    &

@@

            \end{array}\right) & :      & \frametype[n][0,...,p]                             \\
    \framep[n][0,]                                                                         &

@@

    \framep[n][0,...,p+1]                                                                  &

@@

@@

      \Sigma \restrf[n+1][0,...,p-1]
      :\restrftype[n+1][0,...,p-1]

@@

              \restrf[n+1][0,...,p-1]:\restrftype[n][0,...,p-1] \\

@@

                                                                                           & \defeq & \framep[n][p]

@@

              \restrf[n+1][0,...,p-1]:\restrftype[n][0,...,p-1] \\
            \end{array}\right)                                   & :      & \layertype[n][p](\framep[n][0,...,p])           \\

@@

\begin{align*}
  \depstype[n][0,..,p-1] \defeq
  \left(\begin{array}{lll}
            \framep[n][0,...,p-1]   & : & \frametype[n][0,...,p-1]    \\
            \painting[n][0,...,p-1] & : & \paintingtype[n][0,...,p-1]
            (\framep[n][0,...,p-1])                                   \\
            \restrf[n][0,...,p-1]   & : & \restrftype[n][0,...,p-1]
            \left(\begin{array}{l}
                \framep[n][0,...,p-1]   \\
                \painting[n][0,...,p-1] \\
              \end{array}\right)                             \\
          \end{array}\right)
\end{align*}
so that the type of $\framep[n][0,...,p]$ can be shortened into $\depstype[n][0,..,p-1] \rightarrow \frametype[n][0,...,p]$ and similarly for $\layertype[n][p]$ and $\layer[n][p]$.
Later, we shall write $\deps.\framep$, $\deps.\painting$, $\deps.\restrf$ for the corresponding projections of a $\deps$. By abuse of notation, we also write $\unitpoint$ for the only inhabitant of $\depstype[n][0,..,0-1]$.

Defining $\painting[n][p]$, in addition to the type dependency in $\framep[n][p]$, requires the definition of $\painting[n-1][p-1]$, thus also $\framep[n-1][p-1]$ by typing dependency, as well as $\restrf[n][p-1]$. Since $\painting[n][p]$ also depends on $\painting[n][p+1]$ when $p<n$, these dependencies are actually between $\painting[n][p,...,n]$, $\painting[n-1][p,...,n-1]$, $\framep[n][p,...,n]$, $\framep[n-1][p,...,n-1]$ and $\restrf[n][p,...,n]$. Also, for the case $p=n$, this also requires the assumption of an inhabitant $X_{n}$ of $\nu$Set$^{=n}$. Finally, $\framep[n][p,...,n]$, $\framep[n-1][p,...,n-1]$ and $\restrf[n][p,...,n-1]$ respectively depend on the earlier values $\framep[n][0,...,p-1]$, $\framep[n-1][0,...,p-1]$ and $\restrf[n][0,...,p-1]$.  Below, we use dashed underline and dashed arrows for dependencies in subconstructions, here in the construction of $\framep$ at level $n-1$ and $\restrftype$ at level $n$:
\begin{center}
  \fontsize{7.2}{9}\selectfont
  \begin{tikzcd}
    & & \painting[n][p,...,n] \arrow[dd, bend right=70] \arrow[dddr] \arrow[d, dotted]\\
    \udensdash{\framep[n][0,...,p-1]} \arrow[d, dashed] \arrow[ddr, dashed] & &
    \udensdash{\framep[n][p,...,n]} \arrow[ll, dotted] \arrow[d, dashed] \arrow[ddr, dashed, shift right=2mm] \\
    \painting[n-1][0,...,p-1] \arrow[d, dotted] & &
    \painting[n-1][p,...,n-1] \arrow[ll, dotted] \arrow[d, dotted] \\
    \framep[n-1][0,...,p-1] &
    \udensdash{\restrf[n][0,...,p-1]} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm, hook'] &
    \framep[n-1][p,...,n-1] \arrow[ll, dotted, bend left=15] &
    \udensdash{\restrf[n][p,...,n-1]},X_n \arrow[ll, dotted, bend left=15] \arrow[l, dotted] \arrow[uul, dotted, hook']\\
  \end{tikzcd}
\end{center}

Let us introduce another abbreviation to combine a full $\deps[n][0,n]$ with a family $E:\framep[n-1][n-1]\rightarrow \U$:
\begin{align*}
  \fulldepstype[n] \defeq
  \left(\begin{array}{lll}
            \deps[n][0,...,n-1] & : & \depstype[n][0,...,n-1]                          \\
            E                   & : & \frame[n][n](\deps[n][0,...,n-1]) \rightarrow \U \\
          \end{array}\right)
\end{align*}
TODO: say the convention on projection in the Introduction

@@

We can now formally define $\painting[n][p]$ by recursion on $n-p$:
\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \painting[n][p]      &
    (\fulldeps[n-1]:\fulldepstype[n-1])                     \\
    \painting[n][n]      &
    (\fulldeps[n-1])     & \defeq & \fulldeps.E             \\
    \painting[n][p](p<n) &
    (\fulldeps[n-1])     & \defeq & d \mapsto
    \left(\begin{array}{l}
              \Sigma l:\layer(\fulldeps.\deps[n-1][0,...,p-1]). \\
              \painting[n][p+1]
              (\fulldeps[n-1])(d,l)                             \\
            \end{array}\right) \\
  \end{array}
\end{equation*}

From which we can deduce $\painting[n][0,...,p]$ by a second recursion, this time on $p$:

\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \painting[n][0,...,p]   &
    (\fulldeps[n-1])        & :      & \paintingtype[n][0,...,p](\framep[n][0,...,p](\fulldeps.\deps[n-1][0,...,p])) \\
    \painting[n][0,...,0-1] &
    E                       & \defeq & \unittype                                                                     \\
    \painting[n][0,...,p]   &
    (\fulldeps[n-1])
                            & \defeq &
    (\painting[n][0,...,p-1](\fulldeps[n-1]),\painting[n][p](\fulldeps[n-1]))                                        \\
  \end{array}
\end{equation*}

At this stage, we are able to define $\framep[n][0,...,n]$, $\painting[n][0,...,n]$ and $\restrftype[n][0,...,n-1]$ from $\framep[n-1][0,...,n-1]$, $\painting[n-1][0,...,n-1]$ and $\restrf[n-1][0,...,n-1]$, that is from $\deps[n-1][0,...,n-1]$. To go further, we need to define the sequence $\restrptype[n][0,...,p]$ of types of painting restrictions:

\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \restrptype[n][0,...,p]             &
    (\fulldeps[n-1]:\fulldepstype[n-1]) & :      & \U                                                    \\
    \restrptype[n][]                    & E      & \defeq                                    & \unittype \\
    \restrptype[n][0,...,p]             &
    (\fulldeps[n-1])
                                        & \defeq & \restrptype[n+1][0,...,p-1] \times \left(
    \begin{array}{l}
        \Pi q\leq n.\Pi \epsilon.\Pi d:\framep[n][p](\fulldeps.\deps[n][0,...,p]). \\
        \painting[n][p]
        (\fulldeps[n-1])(d) \rightarrow                                            \\ \fulldeps.\deps.\painting[n][p](\fulldeps.\deps.\restrf[n][p][q][\epsilon](d))\end{array}
    \right)                                                                                              \\
  \end{array}
\end{equation*}

Thanks to $\restrptype[n][0,...,n]$, we can mutually define $\restrf[n][p]$ and $\cohftype[n][p]$ from ``full dependencies'', that is from $\frame[n][0,...,n]$, $\painting[n][0,...,n]$, $\restrf[n][0,...,n]$ and some $E:\frame[n+1][n+1]$, using abbreviations in passing for $\layer$ and $\layertype$:

@@

    \restrf[n][0,...,p]                                                          &

@@

                \restrp[n][0,...,p-2]:\restrptype[n][0,...,p-1]

@@

                    \restrp[n][0,...,p-2] \\

@@

      \restrftype[n][0,...,p]

@@

                \framep[n][0,...,p](\fulldeps.\deps[n][0,...,p]) \\
                \painting[n][0,...,p](\fulldeps[n])              \\

@@

    \restrf[n][0,...,0-1]                                                        &

@@

    \restrf[n][0,...,(p+1)-1]                                                    &

@@

                  \fulldeps[n+1]          \\
                  \cohf[n+1][0,...,p-1]   \\

@@

      \Sigma \cohf[n+1][0,...,p-1]
      :\cohftype[n+1][0,...,p-1]

@@

                \fulldeps[n+1]          \\

@@

      \Pi q\leq n.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega.\,\Pi d:\framep[n][p]

@@

                \frame(\fulldeps.\deps[n][0,...,p])     \\
                \painting[n+1][0,...,p-1](\fulldeps[n]) \\
                \restrf[n][0,...,p]

@@

                    \fulldeps[n+1]          \\

@@

@@

              \restrp[n][0,...,p-1]:\restrptype[n][0,...,p-1](\deps[n][0,...,p-1]) \\
              \cohf[n][0,...,p]:\cohftype[n][0,...,p]                              \\

@@

                                                                                 & \defeq & \Pi q \leq n. \Pi \epsilon. \Pi d: \framep[n][p].\left(
        \layer[n][p]\left(

@@

        \layer[n][p](\fulldeps.\deps[n][0,...,n])(\restrf[n][p]

@@

@@

@@

                                \deps[n][0,...,n]     \\

@@

    \lambda q\leq n. \lambda \epsilon.\,\lambda d.\lambda l.\overrightarrow{\cohf[n][p][q][q][\epsilon][\omega](d)}{\restrp[n][p][q][\epsilon](\restrf[n][p][q][\epsilon])(l \omega)} \\

@@

\begin{align*}
  \depscohstype[n][0,..,p-1] \defeq
  \left(\begin{array}{lcl}
            \fulldeps[n][0,...,n] & : & \fulldepstype[n][0,...,n] \\
            \restrp[n][0,...p-1]  & : & \restrptype[n][0,...,p-1] \\
            \cohf[n][0,...,p-1]   & : & \cohftype[n][0,...,p-1]   \\
          \end{array}\right)
\end{align*}
so that the type of $\restrf[n][0,...,p]$ can be rephrased as $\Pi \depscohs[n][0,...,p-1]:\depscohstype[n][0,..,p-1]. \restrftype[n][0,...,p]      \left(\begin{array}{l}
      \depscohs.\fulldeps.\deps.\framep[n][0,...,p]   \\
      \depscohs.\fulldeps.\deps.\painting[n][0,...,p] \\
    \end{array}\right)$, and similarly for $\restrltype$ and $\restrl$. Later, we shall write $\depscohs.\deps$, $\depscohs.\restrp$, and $\depscohs.\cohf$ for the corresponding projections of an element $\depscohs$ in $\depscohstype$. By abuse of notation, we also write $\unitpoint$ for the only inhabitant of $\depscohstype[n][0,..,0-1]$.

It is also convenient to build $\deps$ from $\depscohs$ at the previous level:

\begin{align*}
  \overline{\deps}(\depscohs:\depscohstype) & :      & \depstype \\
  \overline{\deps}(\depscohs)               & \defeq &
  \left(\begin{array}{l}
            \framep[n][p](\depscohs.\fulldeps.\deps[n][0,...,p]) \\
            \painting[n][p](\depscohs.\fulldeps[n][0,...,n])     \\
            \restrf[n][p](\depscohs[n][0,...,p])                 \\
          \end{array}\right)     \\
\end{align*}

\begin{align*}
  \overline{\fulldeps}(\fulldepscohs:\fulldepscohstype) & :      & \fulldepstype \\
  \overline{\fulldeps}(\fulldepscohs)                   & \defeq &
  \left(\begin{array}{l}
            \overline{\deps}(\fulldepscohs.\depscohs) \\
            \fulldepscohs.\depscohs.\fulldeps.E       \\
          \end{array}\right)                                \\
\end{align*}

We need also the notion of full dependencies at the level of coherence conditions, that combines a full $\depscohs[n][0,...,n]$ with a set $E:\framep[n][n](\overline{\deps}(\depscohs[n][0,...,n-1])) \rightarrow \U$:
\begin{align*}
  \fulldepscohstype[n] \defeq
  \left(\begin{array}{lcl}
            \depscohs[n][0,...,n-1] & : & \depscohstype[n][0,...,n-1]                                                \\
            E                       & : & \framep[n+1][n+1](\overline{\deps}(\depscohs[n][0,...,n-1]))\rightarrow \U \\
          \end{array}\right)
\end{align*}
TODO: say the convention on projection in the Introduction

@@

\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \restrp[n][p]                           &
    (\fulldepscohs[n]:\fulldepscohstype[n]) & :      &
    \left(
    \begin{array}{l}
        \Pi q\leq n. \Pi \epsilon. \Pi d:\framep[n][p]
        (\overline{\deps}(\depscohs)).                         \\
        \painting[n][p]
        (\overline{\fulldeps}(\fulldepscohs[n])(d) \rightarrow \\
        \painting[n-1][p](\fulldepscohs.\depscohs.\fulldeps[n])
        (\restrf[n][p](\fulldepscohs.\depscohs[n][0,...,n])(d))\end{array}\right)                                                        \\
    \restrp[n][n]                           &
    (\fulldepscohs[n][0,...,n])             & \defeq & \lambda q\leq n.\lambda \epsilon. \lambda d. \lambda (l,c). l\epsilon \\
    \restrp[n][p](p<n)                      &
    (\fulldepscohs[n][0,...,n])             & \defeq & \lambda q\leq n.\lambda \epsilon. \lambda d. \lambda (l,c).
    \left(\begin{array}{l}
              \restrl[n][p][q][\epsilon](\fulldepscohs.\depscohs[n-1][0,...,p-1])(...)(l), \\
              \restrp[n][p][q][\epsilon]
              (\fulldepscohs[n])(\restrf[n][p](\fulldepscohs.\depscohs[n][0,...,p])(d))(c) \\
            \end{array}\right)                                       \\
  \end{array}
\end{equation*}

@@

...

@@

At this stage, we are then able to define $\restrf$, $\restrp$ and $\cohftype$
from $\depscohs$ at the previous level. To go further, we need to define the
sequence $\cohptype$ of types of painting coherence laws:

\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \cohptype[n][0,...,p] & (\fulldepscohs[n]:\fulldepscohstype[n]) & :      & \U                                      \\
    \cohptype[n][]        & \unitpoint                              & \defeq & \unittype                               \\
    \cohptype[n][0,...,p] & (\fulldepscohs[n])                      & \defeq & \cohptype[n+1][0,...,p-1] \times \left(
    \begin{array}{l}
        \Pi q\leq n.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega.\,\Pi d:...\,\Pi c \\
        \fulldepscohs.\depscohs.\restrp[n][p][q][\epsilon](\restrf(d))(\restrp[n+1][p][r][\omega]
        (\fulldepscohs[n+1])(d)(c)) =                                            \\
        \fulldepscohs.\depscohs.\restrp[n][p][r][\omega](\restrf(d))(\restrp[n+1][p][q+1][\epsilon]
        (\fulldepscohs[n+1])(d)(c))
      \end{array}
    \right)                                                                                                            \\
  \end{array}
\end{equation*}

@@

    \cohf[n][0,...,p]                                                           &

@@

              \cohp[n][0,...,p-2]:\restrptype[n][0,...,p-1](\fulldepscohs[n][0,...,n]) \\
              \coht[n][0,...,p]:\cohttype[n][0,...,p]

@@

            \end{array}\right) & :      & \cohftype[n][0,...,p]                                                                                             \\
    \cohf[n][0]                                                                 &

@@

    \cohf[n][0,...,p+1]                                                         &

@@

              \Sigma \coht[n+1][0,...,p-1]
              :\cohttype[n+1][0,...,p-1]

@@

                  \coht[n+1][0,...,p-1]

@@

              \cohp[n+1][p]:\cohptype[n+1][p]         \\

@@

              \cohp[n][p]       \\

@@

It is also convenient to build $\depscohs$ from $\depscoht$ at the previous level:

\begin{align*}
  \overline{\depscohs}(\depscoht:\depscohttype) & :      & \depscohstype      \\
  \overline{\depscohs}(\depscoht)               & \defeq &
  \left(\begin{array}{l}
            \overline{\deps}[n][p](\depscoht.\fulldepscohs.\depscohs[n][0,...,p]) \\
            \restrp[n][p](\depscoht.\fulldepscohs[n][0,...,n])                    \\
            \cohf[n][p](\depscoht[n][0,...,p])                                    \\
          \end{array}\right) \\
\end{align*}

>>>>

Formally, this can be described as: (NOTE: in frame, p should be understood as (p+1)-1)

@@

    \framep[n+1][0,...,p]                                                                    &

@@

            \end{array}\right) & :      & \frametype[n+1][0,...,p]                             \\
    \framep[n+1][0,...,(0+1)-1]                                                                          &

@@

    \framep[n+1][0,...,((p+1)+1)-1]                                                                  &

@@

                  \restrf[n][0,...,p-1]   \\

@@

      \Sigma \restrf[n][0,...,p-1]
      :\restrftype[n][0,...,p-1]

@@

              \restrf[n][0,...,p]:\restrftype[n][0,...,p] \\

@@

                                                                                           & \defeq & \framep[n+1][p]

@@

              \restrf[n][0,...,p]:\restrftype[n][0,...,p] \\
            \end{array}\right)                                   & :      & \layertype[n][p]
              \restrf[n][0,...,p]:\restrftype[n][0,...,p] \\

@@

\begin{align*}
  \depstype[n][0,..,p-1] \defeq
  \left(\begin{array}{lll}
            \framep[n][0,...,p-1]   & : & \frametype[n][0,...,p-1]    \\
            \painting[n][0,...,p-1] & : & \paintingtype[n][0,...,p-1]
            (\framep[n][0,...,p-1])                                   \\
            \restrf[n][0,...,p-1]   & : & \restrftype[n][0,...,p-1]
            \left(\begin{array}{l}
                \framep[n][0,...,p-1]   \\
                \painting[n][0,...,p-1] \\
              \end{array}\right)                             \\
          \end{array}\right)
\end{align*}
so that the type of $\framep[n+1][0,...,p]$ can be shortened into $\depstype[n][0,..,p-1] \rightarrow \frametype[n+1][0,...,p]$ and similarly for $\layertype[n][p]$ and $\layer[n][p]$.
Later, we shall write $\deps.\framep$, $\deps.\painting$, $\deps.\restrf$ for the corresponding projections of a $\deps$. By abuse of notation, we also write $\unitpoint$ for the only inhabitant of $\depstype[n][0,..,0-1]$.

Defining $\painting[n+1][p]$, in addition to the type dependency in $\framep[n+1][p]$, requires the definition of $\painting[n][p-1]$, thus also $\framep[n][p-1]$ by typing dependency, as well as $\restrf[n][p-1]$. Since $\painting[n+1][p]$ also depends on $\painting[n+1][p+1]$ when $p<n+1$, these dependencies are actually between $\painting[n+1][p,...,n+1]$, $\painting[n][p,...,n]$, $\framep[n+1][p,...,n+1]$, $\framep[n][p,...,n]$ and $\restrf[n][p,...,n]$. Also, for the case $p=n$, this requires the assumption of an inhabitant $X_{n}$ of $\nu$Set$^{=n}$. Finally, $\framep[n+1][p,...,n+1]$, $\framep[n+1][p,...,n]$ and $\restrf[n][p,...,n]$ respectively depend on the earlier values $\framep[n+1][0,...,p-1]$, $\framep[n][0,...,p-1]$ and $\restrf[n][0,...,p-1]$.  Below, we use dashed underline and dashed arrows for dependencies in subconstructions, here in the construction of $\framep$ at level $n$ and $\restrftype$ at level $n$:
\begin{center}
  \fontsize{7.2}{9}\selectfont
  \begin{tikzcd}
    & & \painting[n+1][p,...,n+1] \arrow[dd, bend right=70] \arrow[dddr] \arrow[d, dotted]\\
    \udensdash{\framep[n+1][0,...,p-1]} \arrow[d, dashed] \arrow[ddr, dashed] & &
    \udensdash{\framep[n+1][p,...,n+1]} \arrow[ll, dotted] \arrow[d, dashed] \arrow[ddr, dashed, shift right=2mm] \\
    \painting[n][0,...,p-1] \arrow[d, dotted] & &
    \painting[n][p,...,n-1] \arrow[ll, dotted] \arrow[d, dotted] \\
    \framep[n][0,...,p-1] &
    \udensdash{\restrf[n][0,...,p-1]} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm, hook'] &
    \framep[n][p,...,n] \arrow[ll, dotted, bend left=15] &
    \udensdash{\restrf[n+1][p,...,n]},X_n \arrow[ll, dotted, bend left=15] \arrow[l, dotted] \arrow[uul, dotted, hook']\\
  \end{tikzcd}
\end{center}

Let us introduce another abbreviation to combine a full $\deps[n][0,...,n-1]:\depstype[n][0,...,n-1]$ with a family $E:\framep[n+1][n](\deps[n][0,...,n-1])\rightarrow \U$:
\begin{align*}
  \fulldepstype[n] \defeq
  \left(\begin{array}{lll}
            \deps[n][0,...,n-1] & : & \depstype[n][0,...,n-1]                          \\
            E                   & : & \framep[n+1][n](\deps[n][0,...,n-1]) \rightarrow \U \\
          \end{array}\right)
\end{align*}
TODO: say the convention on projection in the Introduction

@@

We can now formally define $\painting[n+1][p]$ by recursion on $n+1-p$:
\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \painting[n+1][p]      &
    (\fulldeps[n]:\fulldepstype[n])                     \\
    \painting[n+1][n]      &
    (\fulldeps[n])     & \defeq & \fulldeps.E             \\
    \painting[n+1][p](p<n) &
    (\fulldeps[n])     & \defeq & d \mapsto
    \left(\begin{array}{l}
              \Sigma l:\layer[n][p](\fulldeps.\deps[n][0,...,p]). \\
              \painting[n+1][p+1]
              (\fulldeps[n])(d,l)                             \\
            \end{array}\right) \\
  \end{array}
\end{equation*}

From which we can deduce $\painting[n+1][0,...,p]$ by a second recursion, this time on $p$:

\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \painting[n+1][0,...,p]   &
    (\fulldeps[n-1])        & :      & \paintingtype[n+1][0,...,p](\framep[n+1][0,...,p](\fulldeps.\deps[n-1][0,...,p])) \\
    \painting[n+1][0,...,0-1] &
    E                       & \defeq & \unittype                                                                     \\
    \painting[n+1][0,...,p]   &
    (\fulldeps[n-1])
                            & \defeq &
    (\painting[n+1][0,...,p-1](\fulldeps[n-1]),\painting[n+1][p](\fulldeps[n-1]))                                        \\
  \end{array}
\end{equation*}

At this stage, we are able to define $\framep[n+1][0,...,n]$, $\painting[n+1][0,...,n]$ and $\restrftype[n][0,...,n-1]$ from $\framep[n][0,...,n-1]$, $\painting[n][0,...,n-1]$ and $\restrf[n][0,...,n-1]$, that is from $\deps[n][0,...,n-1]$. To go further, we need to define the sequence $\restrptype[n][0,...,p]$ of types of painting restrictions:

\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \restrptype[n][0,...,p-1]             &
    (\fulldeps[n]:\fulldepstype[n]) & :      & \U                                                    \\
    \restrptype[n][0,...,0-1]                & E      & \defeq                                    & \unittype \\
    \restrptype[n][0,...,(p+1)-1]            &
    (\fulldeps[n])
                                        & \defeq & \restrptype[n+1][0,...,p-1] \times \left(
    \begin{array}{l}
        \Pi q\leq n.\Pi \epsilon.\Pi d:\framep[n+1][p](\fulldeps.\deps[n][0,...,p-1]). \\
        \painting[n+1][p]
        (\fulldeps[n])(d) \rightarrow                                            \\ \fulldeps.\deps.\painting[n][p](\fulldeps.\deps.\restrf[n][p][q][\epsilon](d))\end{array}
    \right)                                                                                              \\
  \end{array}
\end{equation*}

Thanks to $\restrptype[n][0,...,p-1]$, we can mutually define $\restrf[n+1][0,...,p]$ and $\cohftype[n][0,...,p-1]$ from ``full dependencies'', that is from $\framep[n][0,...,n]$, $\painting[n][0,...,n]$, $\restrf[n][0,...,n]$ and some $E:\framep[n+1][n](\deps[n][0,...,n-1]) \rightarrow \U$, using abbreviations in passing for $\restrl$ and $\restrltype$:

@@

    \restrf[n+1][0,...,(p+1)-1]                                                          &

@@

                \restrp[n][0,...,p-1]:\restrptype[n][0,...,p-1]
                (\fulldeps[n])    \\

@@

@@

      \restrftype[n+1][0,...,p]

@@

                \framep[n+1][0,...,p](\fulldeps.\deps[n][0,...,p])   \\
                \painting[n+1][0,...,p](\fulldeps[n]) \\

@@

    \restrf[n+1][0,...,(0+1)-1]                                                        &

@@

    \restrf[n+1][0,...,((p+1)+1)-1]                                                    &

@@

                  \cohf[n][0,...,p-1]   \\

@@

    \left\{\begin{array}{l}
      \Sigma \cohf[n][0,...,p-1]
      :\cohftype[n][0,...,p-1]

@@

@@

      \Pi q\leq n.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega.\,\Pi d:\framep[n+2][p]

@@

                \framep[n+1][p](\fulldeps.\deps[n][0,...,p-1])          \\
                \painting[n+1][0,...,p](\fulldeps[n]) \\
                \restrf[n+1][0,...,p]

@@

                  \cohf[n][0,...,p-1] \\

@@

    \end{array}\right.                                                                                        \\

@@

              \restrp[n][0,...,p]:\restrptype[n][0,...,p](\fulldeps[n]) \\

@@

    & \defeq & \Pi q \leq n. \Pi \epsilon. \Pi d: \framep[n+1][p]
    \left(

@@

        \layer[n][p](\fulldeps.\deps[n][0,...,p])(\restrf[n][p]

@@

                  \cohf[n][0,...,p-1]

@@

              \restrp[n][0,...,p]:\restrptype[n][0,...,p](\fulldeps[n]) \\

@@

@@

    \lambda q\leq n. \lambda \epsilon.\,\lambda d.\lambda l.\overrightarrow{\cohf[n][p][q][q][\epsilon][\omega](d)}{\restrp[n][p][q][\epsilon](\restrf[n][p][q][\epsilon]\left(\begin{array}{l}
                  \cohf[n][0,...,p-1]
                \end{array}\right)(d))(l \omega)}                          \\

@@

\begin{align*}
  \depscohstype[n][0,..,p-1] \defeq
  \left(\begin{array}{lcl}
            \fulldeps[n][0,...,n] & : & \fulldepstype[n][0,...,n] \\
            \restrp[n][0,...p-1]  & : & \restrptype[n][0,...,p-1] \\
            \cohf[n][0,...,p-1]   & : & \cohftype[n][0,...,p-1]   \\
          \end{array}\right)
\end{align*}
so that the type of $\restrf[n+1][0,...,p]$ can be rephrased as $\Pi \depscohs[n][0,...,p-1]:\depscohstype[n][0,..,p-1]. \restrftype[n+1][0,...,p]
      \left(\begin{array}{l}
                \framep[n+1][0,...,p](\fulldeps.\deps[n][0,...,p])   \\
                \painting[n+1][0,...,p](\fulldeps[n]) \\
              \end{array}\right)$, and similarly for $\restrltype$ and $\restrl$. Later, we shall write $\depscohs.\deps$, $\depscohs.\restrp$, and $\depscohs.\cohf$ for the corresponding projections of an element $\depscohs$ in $\depscohstype$. By abuse of notation, we also write $E$ for an inhabitant of $\depscohstype[n][0,..,0-1]$ (standing for a non trivial inhabitant of $\fulldeps[n]$).

It is also convenient to build $\deps$ from $\depscohs$ at the
previous level:
\begin{align*}
  \overline{\deps}(\depscohs[n][0,...,p-1]:\depscohstype[n][0,...,p-1]) & :      & \depstype[n+1][0,...,p] \\
  \overline{\deps}(\depscohs)               & \defeq &
  \left(\begin{array}{l}
            \framep[n+1][0,...,p](\depscohs.\fulldeps.\deps[n][0,...,p-1])   \\
            \painting[n+1][0,...,p](\depscohs.\fulldeps[n]) \\
            \restrf[n+1][0,...,p](\depscohs[n][0,...,p-1])         \\
          \end{array}\right)             \\
\end{align*}

We need also the notion of full dependencies at the level of coherence conditions, that combines a full $\depscohs[n][0,...,n]$ with a set $E:\framep[n+2][n+1](\overline{\deps}(\depscohs[n][0,...,n-1])) \rightarrow \U$:
\begin{align*}
  \fulldepscohstype[n] \defeq
  \left(\begin{array}{lcl}
            \depscohs[n][0,...,n-1] & : & \depscohstype[n][0,...,n-1]                         \\
            E                       & : & \framep[n+2][n+1](\overline{\deps}(\depscohs[n][0,...,n-1]))\rightarrow \U \\
          \end{array}\right)
\end{align*}
TODO: say the convention on projection in the Introduction

We can then extend $\overline{\deps}$ to build $\fulldeps$ from $\fulldepscohs$:
\begin{align*}
  \overline{\fulldeps}(\fulldepscohs[n]:\fulldepscohstype[n]) & :      & \fulldepstype[n+1] \\
  \overline{\fulldeps}(\fulldepscohs[n])               & \defeq &
  \left(\begin{array}{l}
            \overline{\deps}(\fulldepscohs.\depscohs[n][0,...,n-1])\\
            \fulldepscohs.\depscohs.\fulldeps.E\\
          \end{array}\right)             \\
\end{align*}

@@

\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \restrp[n+1][p]                           &
    (\fulldepscohs[n]:\fulldepscohstype[n]) & :      &
    \left(
    \begin{array}{l}
        \Pi q\leq n. \Pi \epsilon. \Pi d:\framep[n+2][p]
        (\overline{\deps}(\fulldepscohs.\depscohs[n][0,...,p-1])).    \\
        \painting[n+2][p]
        (\overline{\fulldeps}(\fulldepscohs[n]))(d) \rightarrow \\
        \painting[n+1][p](\fulldepscohs.\depscohs.\fulldeps[n])
          (\restrf[n+1][p](\fulldepscohs.\depscohs[n][0,...,p-1])(d))\end{array}\right)                                       \\
    \restrp[n+1][n]                           &
    (\fulldepscohs[n])             & \defeq & \lambda q\leq n.\lambda \epsilon. \lambda d. \lambda (l,c). l\epsilon \\
    \restrp[n+1][p](p<n)                      &
    (\fulldepscohs[n])             & \defeq & \lambda q\leq n.\lambda \epsilon. \lambda d. \lambda (l,c).
    \left(\begin{array}{l}
      \restrl[n][p][q][\epsilon](\fulldepscohs.\depscohs[n][0,...,p])(d)(l),               \\
              \restrp[n+1][p+1][q][\epsilon](\fulldepscohs[n])(d,l)(c) \\
            \end{array}\right)                              \\
  \end{array}
\end{equation*}

@@

\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \restrp[n+1][0,...,p]   &
    (\fulldepscohs[n])        & :      & \restrptype[n+1][0,...,p](\fulldepscohs.\depscohs.\fulldeps[n])) \\
    \restrp[n+1][0,...,0-1] &
    E  & \defeq & \unittype                                                                   \\
    \restrp[n+1][0,...,p]   &
    (\fulldepscohs[n])
                            & \defeq &
    (\restrp[n+1][0,...,p-1](\fulldepscohs[n]),\restrp[n+1][p](\fulldepscohs[n]))                                        \\
  \end{array}
\end{equation*}

@@

At this stage, we are then able to define $\restrf[n+1][0,...,p]$, $\restrp[n+1][0,...,p]$ and $\cohftype[n][0,...,p]$
from $\depscohs[n][0,...,p-1]$ at the previous level. To go further, we need to define the
sequence $\cohptype[n][0,...,p-1]$ of types of painting coherence laws:

\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \cohptype[n][0,...,p-1] & (\fulldepscohs[n]:\fulldepscohstype[n]) & :      & \U                                      \\
    \cohptype[n][0,...,0-1]        & \unitpoint                                        & \defeq & \unittype                               \\
    \cohptype[n][0,...,(p+1)-1] & (\fulldepscohs[n])                           & \defeq & \cohptype[n][0,...,p-1](\fulldepscohs[n]) \times \left(
    \begin{array}{l}
        \Pi q\leq n.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega.\,\Pi d:\framep[n+2][p](\overline{\deps}(\fulldepscohs.\depscohs[n][0,...,p-1])).\,\Pi c:\painting[n+2][p](\overline{\fulldeps}(\fulldepscohs[n]))\\
        \fulldepscohs.\depscohs.\restrp[n][p][q][\epsilon](\restrf[n+1][p](d))(\restrp[n+1][p][r][\omega]
        (\fulldepscohs[n])(d)(c)) =                         \\
        \fulldepscohs.\depscohs.\restrp[n][p][r][\omega](\restrf[n+1][p](d))(\restrp[n+1][p][q+1][\epsilon]
        (\fulldepscohs[n])(d)(c))
      \end{array}
    \right)                                                                                                            \\
  \end{array}
\end{equation*}

@@

    \cohf[n+1][0,...,p]                                                           &

@@

              \coht[n][0,...,p-1]:\cohttype[n][0,...,p-1]

@@

            \end{array}\right) & :      & \cohftype[n+1][0,...,p]                                                                                             \\
    \cohf[n][0,...,(0+1)-1]                                                           &

@@

    \cohf[n][0,...,((p+1)+1)-1]                                                         &

@@

              \Sigma \coht[n][0,...,p-1]
              :\cohttype[n][0,...,p-1]

@@

                  \coht[n][0,...,p-1]

@@

              \cohp[n][0,...,p]:\cohptype[n][0,...,p]         \\

@@

@@

It is also convenient to build $\depscohs[n+1][0,...,p]$ from $\depscoht[n][0,...,p]$ at the previous level:

\begin{align*}
  \overline{\depscohs}(\depscoht[n][0,...,p]:\depscohttype[n][0,...,p]) & :      & \depscohstype[n+1][0,...,p] \\
  \overline{\depscohs}(\depscoht[n][0,...,p])               & \defeq &
  \left(\begin{array}{l}
            \overline{\deps}(\depscoht.\fulldepscohs.\depscohs[n][0,...,p-1])   \\
            \restrp[n+1][p](\depscoht.\fulldepscohs[n][0,...,n]) \\
            \cohf[n+1][p](\depscoht[n][0,...,p-1])         \\
          \end{array}\right)             \\
\end{align*}
